|

### 2021-09-04 article/articleCustomerDropoutMembership.Rmd
upd

---
title: |
  |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. Quality of Life Research Centre, Polytechnic Institute of Santarém, Portugal]\vspace{0.5cm}
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article. Here we can place more info.\vspace{.8cm}
bibliography: refMembership.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
    number_sections: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{hyperref}
editor_options: 
  markdown: 
    wrap: 80
---

@@

```{python createModel, eval=TRUE, echo=FALSE, cache = TRUE, warning = FALSE}
from pysurvival.models.survival_forest import RandomSurvivalForestModel

# Number of samples in the dataset
N = df_members.shape[0]

# Building training and testing sets
from sklearn.model_selection import train_test_split
index_train, index_test = train_test_split( range(N), test_size = 0.4)
data_train = df_members.loc[index_train].reset_index( drop = True )
data_test  = df_members.loc[index_test].reset_index( drop = True )

# Creating the X, T and E inputs
X_train, X_test = df_members[features], data_test[features]
T_train, T_test = df_members[time_column], data_test[time_column]
E_train, E_test = df_members[event_column], data_test[event_column]

@@

The model was built with with 60% of the data for training and 40% for testing.
The survival model parameters where:

```{python pysurvivalperformance, eval=TRUE, echo=FALSE, cache=FALSE, warning = FALSE}
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

c_index = concordance_index(csf, X_test, T_test, E_test)

ibs = integrated_brier_score(csf, X_test, T_test, E_test, t_max=12,
    figure_size=(12,5))

results = compare_to_actual(csf, X_test, T_test, E_test, is_at_risk = False,  
figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])
```

@@

```{python elbowCalculation, eval=TRUE, echo=FALSE, cache=TRUE, warning = FALSE}
from sklearn.cluster import KMeans
from sklearn import preprocessing
from scipy.spatial.distance import cdist
import matplotlib.pyplot as plt

@@

TODO: fit the model for the five clusters... compare the performance with the model without
clusters... corrigir acima para selecionar só as features

>>>>

---
title: |
  |
  |
  |
  | \vspace{1cm}Customer dropout membership^[Corresponding address: sobreiro@esdrm.ipsantarem.pt. Quality of Life Research Centre, Polytechnic Institute of Santarém, Portugal]\vspace{0.5cm}
author: |
  | Pedro Sobreiro, Javier Berrocal, Domingos Martinho, José Garcia Alonso
  |
  | Extremadura University
  |
date: |
  |
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}Abstract of the article. Here we can place more info.\vspace{.8cm}
bibliography: refMembership.bib
csl: american-sociological-association.csl
output:
  bookdown::word_document2:
    latex_engine: xelatex
    number_sections: true
  bookdown::pdf_document2:
    includes:
    toc: no
    keep_tex: true
    latex_engine: xelatex
    number_sections: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin = 1in
always_allow_html: yes
header-includes:
   - \usepackage{dcolumn}
   - \usepackage{color}
   - \usepackage{pdfpages}
   - \usepackage{amsmath}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{hyperref}
editor_options: 
  markdown: 
    wrap: 80
---

@@

```{python createModel, eval=TRUE, echo=FALSE, cache = FALSE, warning = FALSE}
from pysurvival.models.survival_forest import RandomSurvivalForestModel
from sklearn.model_selection import train_test_split
from pysurvival.utils.metrics import concordance_index
from pysurvival.utils.display import integrated_brier_score
from pysurvival.utils.display import compare_to_actual

X = df_members.copy()
t = df_members['years_membership']
e = df_members['dropout']
X.drop(axis=1, columns=['years_membership','dropout'])

X_train, X_test, t_train, t_test, e_train, e_test = train_test_split(X, t, e, test_size=0.3, random_state=0)

# Fitting the model
csf = RandomSurvivalForestModel(num_trees=200)
csf.fit(X_train, t_train, e_train, max_features='sqrt', max_depth=5, min_node_size=20)

c_index = concordance_index(csf, X_test, t_test, e_test)
ibs = integrated_brier_score(csf, X_test, t_test, e_test, t_max=12, figure_size=(12,5))
results = compare_to_actual(csf, X_test, t_test, e_test, is_at_risk = False,  figure_size=(12, 6), metrics = ['rmse', 'mean', 'median'])
```

@@

The model was built with with 70% of the data for training and 30% for testing.
The survival model parameters where:

@@

```{python elbowCalculation, eval=TRUE, echo=FALSE, cache=FALSE, warning = FALSE}
from sklearn.cluster import KMeans
from sklearn import preprocessing
from scipy.spatial.distance import cdist
import matplotlib.pyplot as plt

@@

TODO: Estava aqui... fit the model for the five clusters... compare the performance with the model without
clusters... corrigir acima para selecionar só as features.. Explorart-SNE for better visualization...
